### 2016-07-15 Projects/DelCo_2012/Report/DelCo_2012.tex
update channel groupings, axis for plots, CAFS report

The fire suppression series included 20 experiments in the single-story experimental structures and one two-story structure. Tweleve experiments were conducted in the single story structures (6 in each structure) using both water and CAF application as a suppression agent. The nozzle patterns were varied and included; straight stream, solid stream, and narrow fog.  The two-story tests used both water and CAF from a straight-stream nozzle.

@@

\begin{figure}[!ht]
	\includegraphics[width=.35\columnwidth]{../Figures/Floor_Plans/PDFs/DelCo_2012_Instrumentation_Legend.pdf}
	\caption{Instrumentation Legend.}
	\label{fig:Instrumentation_Legend}
\end{figure}

@@

In June of 2015, the larger compartment experiments, experiments 13 through 20, were conducted in the lower level of the two story structure.  Two different fuel packages were utitlized, the difference between the furniture fuel package used for experiments 13 and 14, and the furnitiure and pallet fuel package used in experiments 15 through 20 was the addition of two stacks of pallets.

@@

The fuel load for two of the experiments consisted of three sofas with an average mass of 48.7~kg; 51.4~m$^2$ (559~ft$^2$) of carpet and padding; and approximately 38 sheets of oriented strand board (OSB) paneling with dimensions 16~mm (0.63~in) x 1.2~m (4~ft) x 2.4~m (8~ft) along the East, West, and South walls and ceiling. The three couches are aligned along the West wall and spaced 1.2~m (4~ft) apart. The specific locations can be found in the dimensioned schematic, Fig.~\ref{fig:furniture_2story}. In total, this fuel package was composed of wood, flexible polyurethane (PU), polyester (PE),and polyprolene (PP).

@@

The results are arranged in the order that the experiments were conducted.  For the fire suppression experiments, the fuel load and resulting fire hazard were intended to increase as the different structures and fuel packages were utilitized.

@@

Spray density experiments were conducted by placing 0.23~m$^2$ (2.5~ft$^2$) interlocking water colection pans across the floor surface area of the burn rooms within each structure (cf. Fig~\ref{fig:water_buckets}). The depth of the pans was 0.3 m (1 ft).  Water or CAF was flowed for a specified duration or until it appeared that a pan might be filled.  Upon completion the bins were removed from the structure. Each bin was then weighed to quantify the impact of nozzle location and spray pattern. Thirty-three spray density tests were conducted; 21 were in the burn building for the gas cooling tests and 12 were in the single story structure for the suppression experiments. The interior of the fire room in the single story structure was sheathed in plastic for the spray density tests to protect the gypsum board from being soaked with water prior to the fire suppression experiments.  The flow rate for each test was 120~gpm for water and 120~gpm plus 60~cfm for CAF. Tables\ref{tab:spray_density_tests} and \ref{tab:spray_density_tests2} provide an overview of each experiment. In the table, GC stands for the gas cooling experiments while SE stands for the suppression experiments. For all of the experiments, 100~ft (30~m) of 1~3/4~inch hoseline connected to a Blitz Fire monitor with a Metro 1 nozzle was used.

@@

\begin{figure}[ht!]
	\includegraphics[width=\columnwidth]{../Figures/Gas_Cooling/GCSeries4_TC_A3}
	\caption{Time Series of Multiple Gas Cooling Eexperiments from 1 of 9 Burn sequences}
	\label{fig:gas_cooling_exp4}
\end{figure}

There were three thermocouple arrays in the gas cooling room (adjacent to the burn room in Fig.~\ref{fig:Gas_Cooling_Instrumentation_Dimensions}). Figures~\ref{fig:gas_cooling_sub1} and \ref{fig:gas_cooling_sub5} show the variation of the impact of the suppression stream on cooling location for three consecutive water and CAF tests, respectively. For both sets a solid 7/8~in nozzle in the middle position was used. The data shows that thermocouples from Gas Cooling Array 2 (GC\_2 in the legend), the middle plot of both figures, has more significant temperature decreases than the other two arrays (GC\_1 and GC\_3); this is the result of Gas Cooling Array 2 being directly ``hit'' by the suppression stream.  Gas Cooling Array 1 was exhibits some amount of suppression agent impact.  Gas Cooling Array 3 is located behind the area where the stream impacts the celing for both the middle and back nozzle positions.  As a result it remains dry and it seems to provide the best representation of the gas cooling.

@@

Table~\ref{tab:Test_Results} provides the impact of the two nozzle applications for the water and CAF tests. The table provides change in temperature 0.3~m (1~ft) below the ceiling and 0.3~m (1~ft) above the floor as well as change in heat flux 0.15~m (6~in) above the floor at the measurement location closest to the fire. These values reported in the table are immediately before and after the 15~s application period to assess the application agent, stream, and location on interior conditions.  Remeber that there was a 15~s gap between the hallway nozzle flow and the fire room nozzle flow.  As a result you can see the amount of temperature change during the period in between nozzle flows by comparing the temperature at the end of the hallway flow period with the temperature at the beginning of the room flow period.

@@

\begin{figure}[!ht]
	\includegraphics[width=.85\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Instrumentation2}
	\caption{Schematic Indicating Thermcouple Arrays A1 and A2 for Fire Suppression Experiments}
	\label{fig:fs_instruments}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/FSE_Test_1_092812_TC_A2}
	\caption{Time Series of Thermcouple Data from Array TC A2 from Single Story CAF~1 Fire Suppression Test}
	\label{fig:caf1_tca2}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/FSW_Test_2_092812_TC_A2}
	\caption{Time Series of Thermcouple Data from Array TC A2 from Single Story Water~1 Fire Suppression Test}
	\label{fig:water1_tca2}
\end{figure}

Similar to the gas cooling tests, the impact of water and CAF during fire suppression can be analyzed by comparing the temperature differences during the suppression interval at the two the thermocouple arrays in the fire room. Figures~\ref{fig:fs_hall_a1} and \ref{fig:fs_door_a1} show the temperature difference comparison at thermocouple array A1 for CAF and water after the hallway nozzle was activated and then the doorway nozzle was actived, respectively.

@@

In Fig.~\ref{fig:fs_hall_a1}, the red dashed line (linear fit to the data, see Section~\ref{sec:Gas_Cooling}) closely follows the black line, indicates near equal cooling between CAF and water. The R$^2$ value of 0.901 shows a strong fit to the data. When the second nozzle is activated (doorway nozzle), note that the temperature differences are noticabley lower compared to the hallway nozzle, despite it being an indirect attack. While the fit is not as strong (R$^2$ = 0.643), the red line still falls within the experimental uncertainty, meaning that differences in the impact of CAF and water are indistinguishable. Despite being closer to the nozzles, thermocouple tree A2 shows similar the temperature difference results from the hallway nozzle activation to the A1 array (cf. Fig~\ref{fig:fs_door_a1}). At array A2, Fig.~\ref{fig:fs_door_a2}, for doorway nozzle, the red dashed falls outside of the experimental uncertainty, indicating a slight advantage of cooling for CAF.

@@

This study focused on two key types of fire experiments; gas cooling and fire suppression. In each type of experiment a comparison was conducted between plain water and compressed air foam being discharged from nozzles of similar type with similar mass flow rates. In both types of experiments there were no significant measurable differences between the use of plain water or compressed air foam. These results were not surprising to some of the technical panel members. However other members, that use CAF very successfully in their fire departments every day, had additional questions. The research team worked to address those follow-up questions by conducting additional fire suppression experiments.  One experiemntal used only wood based fuels, to examine the value of the reduced surface tension of the water in the CAF and its interaction with the surface of the wood fuel.  A final experimental series, used a larger fire room, with more ventilation.  In addition, the nozzle was hand held and could be moved as needed to effectively extinguish the fire.  This section will discuss the results and provide potential explanations to support them.

@@

Under the given conditions of a residential scale room and the mass of water introduced into the hot gas layer, it should be no suprised that the water is doing the work. Air filled bubbles in the CAFS stream had no discernible impact in these experiments.
At the same time there was no measurable negative effect of the air bubbles with regard to gas cooling.

@@

\subsection{Iowa State Univeristy Fire Flow Formula (1963)}
The Iowa Formula for determining the required fire flowrate for a given structure was developed, by Keith Royer and Bill Nelson, based on theoretical heat absorption capabilities of water. The required fire flowrate in gpm is equal to the volume of the fire compartment (in cubic feet) divided by 100:
\begin{equation}\label{eq:isu_form}
required fire flowrate = Volume / 100
\end{equation}
Due to inefficiencies in applying the water, some feel that the fire flow value from the Iowa State University formula should be multiplied by a factor of two to four~\cite{NFPA}. Applying the  based on floor area yields an application density of 3.3~Lpm/m$^2$ (0.08~gpm/ft$^2$) for ceiling heights of 2.44~m (8~ft) or 4.1~Lpm/m$^2$ (0.10~gpm/ft$^2$) for ceiling heights of 3.05~m (10~ft). Our fire rooms ranged in floor area from approximately 66~m$^3$ (2330~ft$^3$) to 125~m$^3$ (4410~ft$^3$). Therefore the required flowrate for the fire room in the single story structure based on the Iowa State University formula would be approximately 87~Lpm (23~gpm). The required flowrate for the fire room in the lower level of the two story would be approximately 168~Lpm (44~gpm).

@@

The flowrate used for these experiments were sufficent to quickly cool the hot gas layer and suppress each of the fires.

@@

\begin{figure}[ht]
\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/FSE_Test_1_092812_TC_A1}
\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/FSE_Test_1_092812_TC_A2}
\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/FSE_Test_1_092812_TC_A3}
\caption{Thermocouple Data for Arrays in the Fire Room (top - A1, middle - A2) and in the Hallway (bottom - A3) for Single-Story Fire Suppression Test CAF~1}
\end{figure}

>>>>

The fire suppression series included 20 experiments in the single-story experimental structures and one two-story structure. Twelve experiments were conducted in the single story structures (6 in each structure) using both water and CAF application as a suppression agent. The nozzle patterns were varied and included; straight stream, solid stream, and narrow fog.  The two-story tests used both water and CAF from a straight-stream nozzle.

@@

\begin{figure}[!ht]
	\includegraphics[width=.35\columnwidth]{../Figures/Floor_Plans/PDFs/DelCo_2012_Instrumentation_Legend}
	\caption{Instrumentation Legend.}
	\label{fig:Instrumentation_Legend}
\end{figure}

@@

In June of 2015, the larger compartment experiments, experiments 13 through 20, were conducted in the lower level of the two story structure.  Two different fuel packages were utilized, the difference between the furniture fuel package used for experiments 13 and 14, and the furniture and pallet fuel package used in experiments 15 through 20 was the addition of two stacks of pallets.

@@

The fuel load for two of the experiments consisted of three sofas with an average mass of 48.7~kg; 51.4~m$^2$ (559~ft$^2$) of carpet and padding; and approximately 38 sheets of oriented strand board (OSB) paneling with dimensions 16~mm (0.63~in) x 1.2~m (4~ft) x 2.4~m (8~ft) along the East, West, and South walls and ceiling. The three couches are aligned along the West wall and spaced 1.2~m (4~ft) apart. The specific locations can be found in the dimensioned schematic, Fig.~\ref{fig:furniture_2story}. In total, this fuel package was composed of wood, flexible polyurethane (PU), polyester (PE),and polypropylene (PP).

@@

The results are arranged in the order that the experiments were conducted.  For the fire suppression experiments, the fuel load and resulting fire hazard were intended to increase as the different structures and fuel packages were utilized.

@@

Spray density experiments were conducted by placing 0.23~m$^2$ (2.5~ft$^2$) interlocking water collection pans across the floor surface area of the burn rooms within each structure (cf. Fig~\ref{fig:water_buckets}). The depth of the pans was 0.3 m (1 ft).  Water or CAF was flowed for a specified duration or until it appeared that a pan might be filled.  Upon completion the bins were removed from the structure. Each bin was then weighed to quantify the impact of nozzle location and spray pattern. Thirty-three spray density tests were conducted; 21 were in the burn building for the gas cooling tests and 12 were in the single story structure for the suppression experiments. The interior of the fire room in the single story structure was sheathed in plastic for the spray density tests to protect the gypsum board from being soaked with water prior to the fire suppression experiments.  The flow rate for each test was 120~gpm for water and 120~gpm plus 60~cfm for CAF. Tables\ref{tab:spray_density_tests} and \ref{tab:spray_density_tests2} provide an overview of each experiment. In the table, GC stands for the gas cooling experiments while SE stands for the suppression experiments. For all of the experiments, 100~ft (30~m) of 1~3/4~inch hoseline connected to a Blitz Fire monitor with a Metro 1 nozzle was used.

@@

\begin{figure}[ht!]
	\includegraphics[width=\columnwidth]{../Figures/Gas_Cooling/GCSeries4_TC_A3}
	\caption{Time Series of Multiple Gas Cooling Experiments from 1 of 9 Burn sequences}
	\label{fig:gas_cooling_exp4}
\end{figure}

There were three thermocouple arrays in the gas cooling room (adjacent to the burn room in Fig.~\ref{fig:Gas_Cooling_Instrumentation_Dimensions}). Figures~\ref{fig:gas_cooling_sub1} and \ref{fig:gas_cooling_sub5} show the variation of the impact of the suppression stream on cooling location for three consecutive water and CAF tests, respectively. For both sets a solid 7/8~in nozzle in the middle position was used. The data shows that thermocouples from Gas Cooling Array 2 (GC\_2 in the legend), the middle plot of both figures, has more significant temperature decreases than the other two arrays (GC\_1 and GC\_3); this is the result of Gas Cooling Array 2 being directly ``hit'' by the suppression stream.  Gas Cooling Array 1 was exhibits some amount of suppression agent impact.  Gas Cooling Array 3 is located behind the area where the stream impacts the ceiling for both the middle and back nozzle positions.  As a result it remains dry and it seems to provide the best representation of the gas cooling.

@@

Table~\ref{tab:Test_Results} provides the impact of the two nozzle applications for the water and CAF tests. The table provides change in temperature 0.3~m (1~ft) below the ceiling and 0.3~m (1~ft) above the floor as well as change in heat flux 0.15~m (6~in) above the floor at the measurement location closest to the fire. These values reported in the table are immediately before and after the 15~s application period to assess the application agent, stream, and location on interior conditions. Remember that there was a 15~s gap between the hallway nozzle flow and the fire room nozzle flow. The amount of temperature change during the period in between nozzle flows is shown by comparing the temperature at the end of the hallway flow period with the temperature at the beginning of the room flow period.

@@

\begin{figure}[!ht]
	\includegraphics[width=.85\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Instrumentation2}
	\caption{Schematic Indicating Thermocouple Arrays A1 and A2 for Fire Suppression Experiments}
	\label{fig:fs_instruments}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/FSE_Test_1_092812_TC_A2}
	\caption{Time Series of Thermocouple Data from Array TC A2 from Single Story CAF~1 Fire Suppression Test}
	\label{fig:caf1_tca2}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/FSW_Test_2_092812_TC_A2}
	\caption{Time Series of Thermocouple Data from Array TC A2 from Single Story Water~1 Fire Suppression Test}
	\label{fig:water1_tca2}
\end{figure}

Similar to the gas cooling tests, the impact of water and CAF during fire suppression can be analyzed by comparing the temperature differences during the suppression interval at the two the thermocouple arrays in the fire room. Figures~\ref{fig:fs_hall_a1} and \ref{fig:fs_door_a1} show the temperature difference comparison at thermocouple array A1 for CAF and water after the hallway nozzle was activated and then the doorway nozzle was activated, respectively.

@@

In Fig.~\ref{fig:fs_hall_a1}, the red dashed line (linear fit to the data, see Section~\ref{sec:Gas_Cooling}) closely follows the black line, indicates near equal cooling between CAF and water. The R$^2$ value of 0.901 shows a strong fit to the data. When the second nozzle is activated (doorway nozzle), note that the temperature differences are noticeably lower compared to the hallway nozzle, despite it being an indirect attack. While the fit is not as strong (R$^2$ = 0.643), the red line still falls within the experimental uncertainty, meaning that differences in the impact of CAF and water are indistinguishable. Despite being closer to the nozzles, thermocouple tree A2 shows similar the temperature difference results from the hallway nozzle activation to the A1 array (cf. Fig~\ref{fig:fs_door_a1}). At array A2, Fig.~\ref{fig:fs_door_a2}, for doorway nozzle, the red dashed falls outside of the experimental uncertainty, indicating a slight advantage of cooling for CAF.

@@

This study focused on two key types of fire experiments; gas cooling and fire suppression. In each type of experiment a comparison was conducted between plain water and compressed air foam being discharged from nozzles of similar type with similar mass flow rates. In both types of experiments there were no significant measurable differences between the use of plain water or compressed air foam. These results were not surprising to some of the technical panel members. However other members, that use CAF very successfully in their fire departments every day, had additional questions. The research team worked to address those follow-up questions by conducting additional fire suppression experiments.  One experimental used only wood based fuels, to examine the value of the reduced surface tension of the water in the CAF and its interaction with the surface of the wood fuel. A final experimental series, used a larger fire room, with more ventilation.  In addition, the nozzle was hand held and could be moved as needed to effectively extinguish the fire. This section will discuss the results and provide potential explanations to support them.

@@

Under the given conditions of a residential scale room and the mass of water introduced into the hot gas layer, it should be no surprise that the water is doing the work. Air filled bubbles in the CAFS stream had no discernible impact in these experiments.
At the same time there was no measurable negative effect of the air bubbles with regard to gas cooling.

@@

\subsection{Iowa State University Fire Flow Formula (1963)}
The Iowa Formula for determining the required fire flowrate for a given structure was developed, by Keith Royer and Bill Nelson, based on theoretical heat absorption capabilities of water. The required fire flowrate in gpm is equal to the volume of the fire compartment (in cubic feet) divided by 100:
\begin{equation}\label{eq:isu_form}
required fire flowrate = Volume / 100
\end{equation}
Due to inefficiencies in applying the water, some feel that the fire flow value from the Iowa State University formula should be multiplied by a factor of two to four~\cite{NFPA}. Applying the  based on floor area yields an application density of 3.3~Lpm/m$^2$ (0.08~gpm/ft$^2$) for ceiling heights of 2.44~m (8~ft) or 4.1~Lpm/m$^2$ (0.10~gpm/ft$^2$) for ceiling heights of 3.05~m (10~ft). Our fire rooms ranged in floor area from approximately 66~m$^3$ (2330~ft$^3$) to 125~m$^3$ (4410~ft$^3$). Therefore the required flowrate for the fire room in the single story structure based on the Iowa State University formula would be approximately 87~Lpm (23~gpm). The required flowrate for the fire room in the lower level of the two story would be approximately 168~Lpm (44~gpm).

@@

The flowrate used for these experiments were sufficient to quickly cool the hot gas layer and suppress each of the fires.

@@

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_1_092812_TC_A1}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_1_092812_TC_A2}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_1_092812_TC_A3}
\caption{Thermocouple Data for Arrays in the Fire Room (top - A1, middle - A2) and in the Hallway (bottom - A3) for Single-Story Fire Suppression Test CAF~1}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_1_092812_Heat_Flux_1}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_1_092812_Heat_Flux_3}
\caption{Heat Flux and Radiometer Data in the Fire Room (top - 1/2) and in the Hallway (bottom - 3/4) for Single-Story Fire Suppression Test CAF~1}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_1_092812_BDP_A3}
\caption{Hallway Velocity Data from Bi-Directional Probes for Single-Story Fire Suppression Test CAF~1}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_2_092812_TC_A1}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_2_092812_TC_A2}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_2_092812_TC_A3}
\caption{Thermocouple Data for Arrays in the Fire Room (top - A1, middle - A2) and in the Hallway (bottom - A3) for Single-Story Fire Suppression Test Water~1}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_2_092812_Heat_Flux_1}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_2_092812_Heat_Flux_3}
\caption{Heat Flux and Radiometer Data in the Fire Room (top - 1/2) and in the Hallway (bottom - 3/4) for Single-Story Fire Suppression Test Water~1}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_2_092812_BDP_A3}
\caption{Hallway Velocity Data from Bi-Directional Probes for Single-Story Fire Suppression Test Water~1}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_3_092812_TC_A1}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_3_092812_TC_A2}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_3_092812_TC_A3}
\caption{Thermocouple Data for Arrays in the Fire Room (top - A1, middle - A2) and in the Hallway (bottom - A3) for Single-Story Fire Suppression Test CAF~2}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_3_092812_Heat_Flux_1}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_3_092812_Heat_Flux_3}
\caption{Heat Flux and Radiometer Data in the Fire Room (top - 1/2) and in the Hallway (bottom - 3/4) for Single-Story Fire Suppression Test CAF~2}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_3_092812_BDP_A3}
\caption{Hallway Velocity Data from Bi-Directional Probes for Single-Story Fire Suppression Test CAF~2}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_4_092912_TC_A1}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_4_092912_TC_A2}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_4_092912_TC_A3}
\caption{Thermocouple Data for Arrays in the Fire Room (top - A1, middle - A2) and in the Hallway (bottom - A3) for Single-Story Fire Suppression Test Water~2}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_4_092912_Heat_Flux_1}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_4_092912_Heat_Flux_3}
\caption{Heat Flux and Radiometer Data in the Fire Room (top - 1/2) and in the Hallway (bottom - 3/4) for Single-Story Fire Suppression Test Water~2}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_4_092912_BDP_A3}
\caption{Hallway Velocity Data from Bi-Directional Probes for Single-Story Fire Suppression Test Water~2}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_6_093012_TC_A1}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_6_093012_TC_A2}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_6_093012_TC_A3}
\caption{Thermocouple Data for Arrays in the Fire Room (top - A1, middle - A2) and in the Hallway (bottom - A3) for Single-Story Fire Suppression Test CAF~3}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_6_093012_Heat_Flux_1}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_6_093012_Heat_Flux_3}
\caption{Heat Flux and Radiometer Data in the Fire Room (top - 1/2) and in the Hallway (bottom - 3/4) for Single-Story Fire Suppression Test CAF~3}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_6_093012_BDP_A3}
\caption{Hallway Velocity Data from Bi-Directional Probes for Single-Story Fire Suppression Test CAF~3}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_5_093912_TC_A1}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_5_093912_TC_A2}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_5_093912_TC_A3}
\caption{Thermocouple Data for Arrays in the Fire Room (top - A1, middle - A2) and in the Hallway (bottom - A3) for Single-Story Fire Suppression Test Water~3}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_5_093912_Heat_Flux_1}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_5_093912_Heat_Flux_3}
\caption{Heat Flux and Radiometer Data in the Fire Room (top - 1/2) and in the Hallway (bottom - 3/4) for Single-Story Fire Suppression Test Water~3}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_5_093912_BDP_A3}
\caption{Hallway Velocity Data from Bi-Directional Probes for Single-Story Fire Suppression Test Water~3}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_8_093912_TC_A1}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_8_093912_TC_A2}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_8_093912_TC_A3}
\caption{Thermocouple Data for Arrays in the Fire Room (top - A1, middle - A2) and in the Hallway (bottom - A3) for Single-Story Fire Suppression Test CAF~4}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_8_093912_Heat_Flux_1}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_8_093912_Heat_Flux_3}
\caption{Heat Flux and Radiometer Data in the Fire Room (top - 1/2) and in the Hallway (bottom - 3/4) for Single-Story Fire Suppression Test CAF~4}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_8_093912_BDP_A3}
\caption{Hallway Velocity Data from Bi-Directional Probes for Single-Story Fire Suppression Test CAF~4}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_7_093012_TC_A1}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_7_093012_TC_A2}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_7_093012_TC_A3}
\caption{Thermocouple Data for Arrays in the Fire Room (top - A1, middle - A2) and in the Hallway (bottom - A3) for Single-Story Fire Suppression Test Water~4}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_7_093012_Heat_Flux_1}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_7_093012_Heat_Flux_3}
\caption{Heat Flux and Radiometer Data in the Fire Room (top - 1/2) and in the Hallway (bottom - 3/4) for Single-Story Fire Suppression Test Water~4}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_7_093012_BDP_A3}
\caption{Hallway Velocity Data from Bi-Directional Probes for Single-Story Fire Suppression Test Water~4}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_12_051613_TC_A1}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_12_051613_TC_A2}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_12_051613_TC_A3}
\caption{Thermocouple Data for Arrays in the Fire Room (top - A1, middle - A2) and in the Hallway (bottom - A3) for Single-Story Fire Suppression Test CAF~5}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_12_051613_Heat_Flux_1}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_12_051613_Heat_Flux_3}
\caption{Heat Flux and Radiometer Data in the Fire Room (top - 1/2) and in the Hallway (bottom - 3/4) for Single-Story Fire Suppression Test CAF~5}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_12_051613_BDP_A3}
\caption{Hallway Velocity Data from Bi-Directional Probes for Single-Story Fire Suppression Test CAF~5}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_11_051613_TC_A1}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_11_051613_TC_A2}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_11_051613_TC_A3}
\caption{Thermocouple Data for Arrays in the Fire Room (top - A1, middle - A2) and in the Hallway (bottom - A3) for Single-Story Fire Suppression Test Water~5}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_11_051613_Heat_Flux_1}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_11_051613_Heat_Flux_3}
\caption{Heat Flux and Radiometer Data in the Fire Room (top - 1/2) and in the Hallway (bottom - 3/4) for Single-Story Fire Suppression Test Water~5}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_11_051613_BDP_A3}
\caption{Hallway Velocity Data from Bi-Directional Probes for Single-Story Fire Suppression Test Water~5}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_14_052013_TC_A1}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_14_052013_TC_A2}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_14_052013_TC_A3}
\caption{Thermocouple Data for Arrays in the Fire Room (top - A1, middle - A2) and in the Hallway (bottom - A3) for Single-Story Fire Suppression Test CAF~6}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_14_052013_Heat_Flux_1}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_14_052013_Heat_Flux_3}
\caption{Heat Flux and Radiometer Data in the Fire Room (top - 1/2) and in the Hallway (bottom - 3/4) for Single-Story Fire Suppression Test CAF~6}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_14_052013_BDP_A3}
\caption{Hallway Velocity Data from Bi-Directional Probes for Single-Story Fire Suppression Test CAF~6}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_13_052013_TC_A1}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_13_052013_TC_A2}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_13_052013_TC_A3}
\caption{Thermocouple Data for Arrays in the Fire Room (top - A1, middle - A2) and in the Hallway (bottom - A3) for Single-Story Fire Suppression Test Water~6}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_13_052013_Heat_Flux_1}
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_13_052013_Heat_Flux_3}
\caption{Heat Flux and Radiometer Data in the Fire Room (top - 1/2) and in the Hallway (bottom - 3/4) for Single-Story Fire Suppression Test Water~6}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_13_052013_BDP_A3}
\caption{Hallway Velocity Data from Bi-Directional Probes for Single-Story Fire Suppression Test Water~6}
\end{figure}
